---
title: "Univariate Viz"
---

```

Use this file for practice with the **univariate viz** in-class activity.  Refer to the class website for details.
```{r}
# Import data
hikes <- read.csv("https://mac-stat.github.io/data/high_peaks.csv")
```
```{r}
# Import data
hikes <- read.csv("https://mac-stat.github.io/data/high_peaks.csv")
```
```{r}
# Import data
hikes <- read.csv("")
```
```{r}
# Import data
survey <- read.csv("https://hash-mac.github.io/stat112site-s25/data/survey.csv")
```
```{r}
hikes <- read.csv(" https://mac-stat.github.io/data/high_peaks.csv")
```
```{r}
hikes <- read.csv("https://mac-stat.github.io/data/high_peaks.csv")
```
```{r}
hikes <- read.csv("https://mac-stat.github.io/data/high_peaks.csv")
```
head(hikes)

head(hikes)


head(hikes)
# Use the ggplot function
ggplot(hikes, aes(x = rating))
# Use the ggplot function
ggplot(hikes, aes(x = rating))
```{r}
# Load the package
library(tidyverse)
```

# COMMENT on the change in the code and the corresponding change in the plot
ggplot(hikes, aes(x = rating)) +
  geom_bar(color = "orange", fill = "blue")  +
  labs(x = "Rating", y = "Number of hikes") +
  theme_minimal()
```{r}
# COMMENT on the change in the code and the corresponding change in the plot
ggplot(hikes, aes(x = rating)) +
  geom_bar(color = "orange", fill = "blue")  +
  labs(x = "Rating", y = "Number of hikes") +
  theme_minimal()
```
```{r}
# COMMENT on the change in the code and the corresponding change in the plot
ggplot(hikes, aes(x = elevation)) +
  geom_histogram(color = "white") 
```

```{r}
# COMMENT on the change in the code and the corresponding change in the plot
ggplot(hikes, aes(x = elevation)) +
  geom_histogram(color = "white", binwidth = 5) +
  labs(x = "Elevation (feet)", y = "Number of hikes")
```

```{r}

```

